Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-05 Experiments.tex
minor fix.
Changed Agent in Pilot Agent and removed NGE's pilot

We measured the execution time of the pilots and of AthenaMP within them,
collecting timestamps at all stages of the execution. Experiments were
performed by submitting NGE's pilots to Titan's batch queue. The turnaround
time of an individual run is determined by queue waiting times. Since we are
interested only in the performances of the NGE, we removed queue time from
our statistics.

@@

Tasks do not wait within the NGE Agent's queue since one node is available to
each AthenaMP instance. Task execution  overheads result primarily from  three
factors: (i) the initial bootstrapping of the pilot on the nodes; (ii) the
UnitManager's dispatching of units (tasks) to the agent; and (iii) time for
the agent to bootstrap all the tasks on the nodes.

We tested pilots with 250, 500, 1000 and 2000 worker nodes and 2 hours
walltime. The time duration is determined by the Titan's walltime policy.
Fig.~\ref{fig:weakScal1a} depicts the average pilot duration, the average
execution time of AthenaMP, and the NGE pilot overhead as function of the
pilot size.

@@

We investigate strong scalability by running the same number of tasks for
different pilot sizes. We used 2048 AthenaMP instances and pilots with 256,
512, 1024 and 2048 nodes. Thus, the number of AthenaMP generations is equal
to eight times the size of the smallest pilot and corresponds to the size of
the largest pilot. As a consequence, the number of consecutive generations of
AthenaMP decreases with the pilot size by generating different dynamics
within the pilots. These experiments are designed to investigate whether
pilot overhead is affected by the degree of concurrency within the pilot
and/or the number of tasks. Each AthenaMP instance simulates sixteen events
as in the previous experiment.

>>>>

We measured the execution time of the pilots and of AthenaMP within them,
collecting timestamps at all stages of the execution. Experiments were
performed by submitting pilots to Titan's batch queue. The turnaround
time of an individual run is determined by queue waiting times. Since we are
interested only in the performances of the NGE, we removed queue time from
our statistics.

@@

Tasks do not wait within the Agent's queue since one node is available to
each AthenaMP instance. Task execution  overheads result primarily from  three
factors: (i) the initial bootstrapping of the pilot on the nodes; (ii) the
UnitManager's dispatching of units (tasks) to the agent; and (iii) time for
the agent to bootstrap all the tasks on the nodes.

We tested pilots with 250, 500, 1000 and 2000 worker nodes and 2 hours
walltime. The time duration is determined by the Titan's walltime policy.
Fig.~\ref{fig:weakScal1a} depicts the average pilot duration, the average
execution time of AthenaMP, and the pilot overhead as function of the
pilot size.

@@

We investigate strong scalability by running the same number of tasks for
different pilot sizes. We used 2048 AthenaMP instances and pilots with 256,
512, 1024 and 2048 nodes. Thus, the number of AthenaMP generations is equal to
eight times the size of the smallest pilot and corresponds to the size of the
largest pilot. As a consequence, the number of consecutive generations of
AthenaMP decreases with the pilot size. These experiments are designed to
investigate whether pilot overhead is affected by the degree of concurrency
within the pilot and/or the number of tasks. Each AthenaMP instance simulates
sixteen events as in the previous experiment.
